Appendix A: Model Validation

### 2021-09-08 doc/validate_models.Rmd
update validation appendix

```{r eval=TRUE}
# Function sourced from R/utils.R
check_res_edf(s_1ha)
```

>>>>

```{r eval=TRUE}
check_res_edf <- function(model) {
  res <- residuals(model)
  mgcv::gam(res ~ te(spei_history, L, k = c(20, 35), bs = "cs"),
      gamma = 1.4,
      data = model.frame(model)) %>%
    gratia::edf() %>% 
    dplyr::mutate(edf = round(edf, 1))
}

check_res_edf(s_1ha)
```
